### 2015-10-27 inst/examples/merge_data.Rmd
merge examples
Much more general and flexible method for get_metadata

```{r}
library("RNeXML")
library("dplyr")
library("geiger")
```

@@

```{r}
otu_meta <- get_metadata(nex, "otu")
taxa <- get_taxa(nex)
char <- get_characters(nex, rownames_as_col = TRUE)
```

@@

```{r}
taxa %>% 
  left_join(char, by = c("label" = "taxa")) %>% 
  left_join(otu_meta, by = c("id" = "parent_id")) %>%
  select(id, label, x, href)
```

>>>>

```{r}
library("RNeXML")
library("dplyr")
library("geiger")
knitr::opts_chunk(message = FALSE, comment = NA)
```

@@

```{r}
otu_meta <- get_metadata(nex, "otus/otu")
taxa <- get_taxa(nex)
char <- get_characters(nex, rownames_as_col = TRUE)
```

We can take a peek at what the tables look like, just to orient ourselves:

```{r}
otu_meta
taxa
head(char)
```

@@

```{r}
taxa %>% 
  left_join(char, by = c("label" = "taxa")) %>% 
  left_join(otu_meta, by = c("id" = "otu")) %>%
  select(id, label, x, href)
```

Because these are all from the same otus block anyway, we haven't selected that column, but were it of interest it is also available in the taxa table.
